Recalibrating Gravitational Wave Phenomenological Waveform Model

### 2024-04-10 src/tex/ms.tex
minor change for submission

The rest of the paper is structured as follows: In Sec.~\ref{sec:method}, we
review the parameterization of the IMRPhenomD model and the mismatch function
that is used as an objective/loss function for the calibration, followed by 
outlining the specific optimization scheme used for recalibration. In
Sec.~\ref{sec:result}, we give the optimization result by comparing mismatches
of the optimized waveforms with the original waveforms. We also show how the
optimization result differs as a function of the source parameters. Finally, in
Sec.~\ref{sec:discussion}, we discuss the differences between our calibration
procedure and the procedure used in \citep{khan2016frequency}. \corr{We point 
out how some caveats, such as the difference in training waveforms, limit our 
conclusion to the mismatch improvement.} We also explain how the reduced spin 
parameterization affects the accuracy of the model. Note that throughout this 
paper we use the terms recalibration and optimization interchangeably.

@@

>>>>

The rest of the paper is structured as follows: In Sec.~\ref{sec:method}, we
review the parameterization of the IMRPhenomD model and the mismatch function
that is used as an objective/loss function for the calibration, followed by 
outlining the specific optimization scheme used for recalibration. In
Sec.~\ref{sec:result}, we give the optimization result by comparing mismatches
of the optimized waveforms with the original waveforms. We also show how the
optimization result differs as a function of the source parameters. Finally, in
Sec.~\ref{sec:discussion}, we discuss the differences between our calibration
procedure and the procedure used in \citep{khan2016frequency}. \corr{Additionally, 
we discuss some caveats (such as the difference in training waveforms) that limit 
our conclusions on the mismatch improvement.} We also explain how the reduced spin 
parameterization affects the accuracy of the model. Note that throughout this 
paper we use the terms recalibration and optimization interchangeably.

@@

\newpage
